---
title: "Chapter 02: Introduction to Ethics"
author: "Aaron Curtis"
date: "October 9, 2015"
output: ioslides_presentation
---

## Chapter Overview

- Introduction
- Review of nine ethical theories
- Comparing workable ethical theories
- Morality of breaking the law

## 2.1 Introduction

## We live in communities

## The Ethical Point of View

- Most everyone shares core values
- Two ways to view the world
  - Selfish point of view
  - Ethical point of view
  
## Defining Terms

- Society
- Morality
- Ethics

## Analogy For Difference Between Society and Ethics

## Why Study Ethics?

## Scenario 1

## Scenario 2

## Scenario 3

## Scenario 4

## More on Ethics

## A Good Ethical Theory Supports Persuasive, Logical Arguments

## 2.2 Subjective Relativism

## What is Relativism?

## Case for Subjective Relativism

## Case Against Subjective Relativism

## 2.3 Cultural Relativism

## Cultural Relativism in a Nutshell

## Case for Cultural Relativism

## Case 


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

